\chapter*{Acknowledgements}

\lettrine[lines=3, lhang=0.15, nindent=0em]{\color{Maroon}M}{any people have helped me during the years,}
and this space is to thank them.
I want to thank my supervisor, Arne Elofsson, for giving me the oportunity to join his lab.
Also for giving me the freedom to explore, always having an open door for discussions and questions, and for putting up with my mistakes.
My gratitude extends to my co-supervisor, Erik Lindahl, for his advice on presentation and communication.
On the topic of supervisors, I am also thankful to Lukas Käll, for introducing me into Bioinformatics in particular, and the practice of science in general, and for getting me the job.

\begin{center}
    \smallskip
    \adfleafleft
    \smallskip
\end{center}

My research on deep learning would not have been possible without Heydar Maboudi Afkham, who gave me the necessary advice with surgical precision to set me on the right path.
And what I had left to learn, I did observing Mirco Michel at work.
I cannot forget Karolis Uziela, for offering his data and opinions during very fruitful discussions on our ongoing projects.
And I thank all my colleagues at work, past and present, for the discussions over lunch over a wide assortment of topics, from pensions to medieval metaphysics. 

\begin{center}
    \medskip
    \adfflowerleft
    \medskip
\end{center}

But work has only been a fraction of the time.
On a personal level, Seméli deserves many thanks for always being there, both helping me and challenging me to be my best.

I also thank both sets of families, back in Spain and the political one, for their unconditional support and help navigating a new country.

\begin{center}
    \medskip
    \adfdownleafright
    \medskip
\end{center}

Finally, a salute to my friends at \textsc{spiff}, for all the mutual poking with metal sticks and keeping the second half of the adage \emph{mens sana in corpore sano}.
Another to the roleplaying troupe, for all the shared assaults on defenceless banana trucks and uncanny valley dolls.
And to everyone who braved the cold and darkness and visited me here.

\bigskip

\raggedleft
Most grateful.

\textsw{\emph{David.}}


