\KOMAoptions{open=left}
\chapter*{Papers included in this thesis}

\section*{Paper \textcolor[cmyk]{0, 0.87, 0.68, 0.32}{I}}
Karolis Uziela\first, David Menéndez Hurtado\first, and Arne Elofsson.
ProQ3D: improved model quality assessments using deep learning. \textit{Bioinformatics}, 33(10):1578–1580, 2017.
\URL \url{ https://doi.org/10.1093/bioinformatics/btw819}.

\section*{Paper  \textcolor[cmyk]{0, 0.87, 0.68, 0.32}{II}}
Mirco Michel, David Menéndez Hurtado, Karolis Uziela, and Arne Elofsson.
Large-scale structure
prediction by improved contact predictions and model quality assessment. \textit{Bioinformatics}, 33(14):
i23–i29, 07 2017.  \URL
\url{https://doi.org/10.1093/bioinformatics/btx239}.


\section*{Paper \textcolor[cmyk]{0, 0.87, 0.68, 0.32}{III}}
Mirco Michel\first, David Menéndez Hurtado\first, and Arne Elofsson. PconsC4: fast, accurate and hassle-free
contact predictions. \textit{Bioinformatics}, 35(15): 2677–2679, 12 2018. \URL \url{https://doi.org/10.1093/bioinformatics/bty1036}.


\section*{Paper \textcolor[cmyk]{0, 0.87, 0.68, 0.32}{IV}}
David Menéndez Hurtado, Karolis Uziela, and Arne Elofsson, A novel training procedure to train deep networks in the assessment of the quality of protein models. \emph{Manuscript}


\section*{Paper \textcolor[cmyk]{0, 0.87, 0.68, 0.32}{V}}

Jianlin Cheng\first, Myong-Ho Choe\first, Arne Elofsson\first, Kun-Sop Han\first, Jie Hou\first, Ali H. A. Maghrabi\first, Liam J.
McGuffin\first, David Menéndez Hurtado\first, Kliment Olechnovič\first, Torsten Schwede\first, Gabriel Studer\first, Karolis
Uziela\first, Česlovas Venclovas\first, and Björn Wallner\first. Estimation of model accuracy in \CASP13. \emph{Proteins}, 2019; 1--17. \URL \url{https://doi.org/10.1002/prot.25767}.

\vspace{2em}
\noindent\first{} indicates shared first author.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\KOMAoptions{open=right}
\chapter*{Other papers not included}


\vspace{2em}

\begin{enumerate}[parsep=3em, topsep=2em]
	\item \bibentry{PconsC3}
	\item \bibentry{casp12_ema}
	\item \bibentry{target_function}
	\item \bibentry{pconsfam}
	\item \bibentry{claudio}
\end{enumerate}
